Results

### 2018-03-15 02_analysis.Rmd
Plot predicted medians

```{r models-predicted}
newdata_conditions <- results %>% 
  expand(nesting(crackdown, issue, funding))

@@

ggplot(newdata, aes(y = estimate, x = funding)) + 
  geom_point(data = all_posterior_draws, aes(y = value, x = funding), 
             color = "grey50", size = 1.5, alpha = 0.25) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high)) + 
  scale_y_continuous(labels = dollar) +
  labs(x = "Funding", y = "Average amount donated") +
  coord_cartesian(ylim = c(0, 100)) +
  theme_ngos() +
  facet_wrap(~ crackdown + issue)
```

>>>>

**Just the crackdown condition**

```{r models-predicted-crackdown}
newdata_conditions <- results %>% expand(nesting(crackdown))

posterior_fit <- posterior_predict(m_amount_crackdown, 
                                   newdata = newdata_conditions,
                                   re.form = NA, draws = 50, seed = BAYES_SEED)

ggplot(newdata, aes(y = estimate, x = crackdown)) + 
  geom_point(data = all_posterior_draws, aes(y = value, x = crackdown), 
             color = "grey50", size = 1.5, alpha = 0.25) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high)) + 
  scale_y_continuous(labels = dollar) +
  labs(x = "Crackdown condition", y = "Median amount donated") +
  coord_cartesian(ylim = c(0, 100)) +
  theme_ngos()
```

**Crackdown and issue conditions**

```{r models-predicted-crackdown-issue}
newdata_conditions <- results %>% expand(nesting(crackdown, issue))

posterior_fit <- posterior_predict(m_amount_crackdown, 
                                   newdata = newdata_conditions,
                                   re.form = NA, draws = 50, seed = BAYES_SEED)

ggplot(newdata, aes(y = estimate, x = crackdown)) + 
  geom_point(data = all_posterior_draws, aes(y = value, x = crackdown), 
             color = "grey50", size = 1.5, alpha = 0.25) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high)) + 
  scale_y_continuous(labels = dollar) +
  labs(x = "Crackdown condition", y = "Median amount donated") +
  coord_cartesian(ylim = c(0, 100)) +
  theme_ngos() +
  facet_wrap(~ issue)
```

**Crackdown, issue, and funding conditions**

```{r models-predicted-crackdown-issue-funding}
newdata_conditions <- results %>% expand(nesting(crackdown, issue, funding))

@@

ggplot(newdata, aes(y = estimate, x = crackdown)) + 
  geom_point(data = all_posterior_draws, aes(y = value, x = crackdown), 
             color = "grey50", size = 1.5, alpha = 0.25) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high)) + 
  scale_y_continuous(labels = dollar) +
  labs(x = "Crackdown condition", y = "Median amount donated") +
  coord_cartesian(ylim = c(0, 100)) +
  theme_ngos() +
  facet_wrap(~ issue + funding)
```
